Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-19 Ch1_movement_rates/Ch1_Figures.Rmd
exploring so many options to try and visualize this.

```{r}
disp_df %>%
  group_by(., model) %>%
  #sample_n(., 5000) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  #sample_n(., 5000) %>%
  ggplot(., aes(y = av.disp, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersal

@@

```{r fig.height=12}

points_plot <- function(seed.data, s.size = 1000, xylims=1250, lalpha = 0.3){
  seed.data %>% 
    drop_na(s.id) %>% 
    mutate(ov500 = ifelse(disp <500, "non", "ldd")) %>% 
    sample_n(s.size) %>% 
      ggplot(., aes(x = xloc, y = yloc, color = ov500)) +
      geom_point(alpha = lalpha) +
      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
      theme_bw()

}

A <- points_plot(seed.data = cp.df)
B <- points_plot(seed.data = pp.df)
C <- points_plot(seed.data = np.df)

plot_grid(A, B, C, nrow = 3)

>>>>

```{r}
disp_df %>%
  group_by(., model) %>%
  sample_n(., 50000) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  sample_n(., 50000) %>%
  ggplot(., aes(y = av.disp, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersal

@@

points_plot <- function(seed.data, summ.data, s.size = 25, xylims=1250, lalpha = 0.5){
  seed.data %>% 
    drop_na(s.id) %>% 
    #mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>% 
    slice_head(., n = s.size) %>% 
    #sample_n(s.size) %>% 
      ggplot(., aes(x = xloc, y = yloc, color = run)) +
      geom_point(alpha = lalpha) +
      #scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
      theme_bw() +
      theme(legend.position = "none",
            axis.title = element_blank()) +
       NULL -> seedlocplot

  summ.data %>%
    #cp.summ.df %>%
    #sample_n(s.size) %>%
    slice_head(., n = s.size/5) %>%
    #pivot_longer(., cols = c(dsprsn, av.disp)) %>%
    #ggplot(., aes(x = name, y = value)) +
    ggplot(., aes(y = dsprsn)) +
    #geom_violin() +
    #geom_jitter(position = position_jitter(0.1), alpha = lalpha) +
    #geom_boxplot(width = 0.1) +
    geom_point(aes(x=0, color = run)) +
    lims(y = c(0, 650)) +
    labs(y = "Dispersion in meters") +
    theme_bw() +
    NULL -> dispersionplot

  plot_grid(seedlocplot, dispersionplot, ncol=2, rel_widths = c(2,1))
  # 
}

A <- points_plot(seed.data = cp.df, summ.data = cp.summ.df)

A

# B <- points_plot(seed.data = pp.df, summ.data = pp.summ.df)
# C <- points_plot(seed.data = np.df, summ.data = np.summ.df)
# 
# plot_grid(A, B, C, ncol = 3)
